---
title: "Trefor 10kV Cables Data Analysis"
output:
  html_document:
    number_sections: yes
    theme: yeti
    toc: yes
    toc_float: yes
---
---
  
```{r headers, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
#BeginHeader
#Input#DataTable#Name:10_15kV Cables Asset Base#Description:10_15kV Cables raw asset data.
#Output#DataTable#Name:10_15kV Cables Population Summary#Description:Summary of population for each field of the data.
#Output#DataTable#Name:10_15kV Cables For Model#Description:10_15kV Cables asset base for the model.
#EndHeader

#rm(list = ls())

EDA <- F  # set to TRUE if running in EDA data labs

if (EDA) {
  args <- commandArgs(trailingOnly = TRUE)
} else {
  args <- c(getwd(),
            "Data/Asset Bases/HV Non-Pressurised Cables_Raw Assets (EDA Version v1) 2207.csv",
            "Output Data/10_15kV Cables Population Summary 2207.csv",
            "Output Data/10_15kV Cables for Model 2207.csv")
}

setwd(args[1])
```


```{r load.data, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
library(tidyverse)
library(data.table)
library(ggplot2)
library(DescTools)
library(knitr)
library(kableExtra)

cables.assets <- data.table(read_csv(args[2], locale=locale(encoding="Latin1")))

## remove any completely empty rows and make asset id unique throughout
cables.assets <- cables.assets[!apply(is.na(cables.assets) | cables.assets == "", 1, all),]
cables.assets$Asset_Number <- make.unique(as.character(cables.assets$Asset_Number))

# calculate average year of manufacture (excluding 0, NA & default values)
cables.assets.copy <- cables.assets
cables.assets.copy$Year_Of_Manufacture[cables.assets.copy$Year_Of_Manufacture==0 |cables.assets.copy$Year_Of_Manufacture=="Default" ] <- NA
average.year <- round(mean(as.numeric(cables.assets.copy$Year_Of_Manufacture), na.rm=T))

##Strip out danish characters to limit problems.
#ae
cables.assets <- cables.assets[, lapply(.SD,   function(x){gsub("Æ", "AE", gsub("æ", "ae", x))}),  .SDcols = 1:ncol(cables.assets)]
names(cables.assets) <- gsub("Æ", "AE", gsub("æ", "ae", names(cables.assets)))

#aa
cables.assets <- cables.assets[, lapply(.SD,   function(x){gsub("Å", "AA", gsub("å", "aa", x))}),  .SDcols = 1:ncol(cables.assets)]
names(cables.assets) <- gsub("Å", "AA", gsub("å", "aa", names(cables.assets)))

#oe
cables.assets <- cables.assets[, lapply(.SD,   function(x){gsub("Ø", "OE", gsub("ø", "oe", x))}),  .SDcols = 1:ncol(cables.assets)]
names(cables.assets) <- gsub("Ø", "OE", gsub("ø", "oe", names(cables.assets)))

cables.assets <- as.tibble(cables.assets)

# define model field names
# model.names <- c("Area1", "TYPE", "Asset_Number", "Health_Index_Asset_Category",     
#                  "Asset_Register_Category","Voltage",    
#                 "Year_Of_Manufacture","SubDivision","Utilisation_Duty_Factor",
#                 "Voltage_Duty_Factor",
#                  "Cable_Safety_Rating","Type_Factor","Network_Type_Factor","Actual_Load",
#                 "Top_30_Customers_Factor","Connected_Customers","KVA_Band_Per_Customer",
#                 "Customer_Sensitivity_Factor","Quantity Resource",
#                 "Sheath Test Factor","Partial Discharge Factor","Fault History Factor",
#                  "Reliability Modifier", "Reliability Collar")

#cables.assets.copy <- cables.assets.copy[, names(cables.assets.copy) %in% model.names]

```

# **Asset Quantity**

There are **`r nrow(cables.assets)`** records in the source data. Ignoring NA or default values:

* The average year of manufacture is **`r average.year`**.

---

# **Population Summary**

The chart below shows the fields provided in each source data item and indicates how populated each field is. An entry is deemed as unpopulated if it is either NA or blank.

```{r warning=FALSE, echo=FALSE, message = FALSE, fig.height = 18}
cables.assets[cables.assets == ""] <-  NA
Unpopulated <- apply(cables.assets, 2, function(x) (mean(is.na(x)))*100)
Default <- apply(cables.assets, 2, function(x) (mean(x %in% c("Default", "default", "DEFAULT")))*100)
Default <- ifelse(is.na(Default), 0, Default)
Populated <- 100 - Unpopulated - Default
Field <- names(Unpopulated)
data.pop <- data.frame(Field, Unpopulated, Populated, Default)
data.pop <- gather(data.pop, variable, value, -Field) %>%
  mutate(variable = factor(variable, levels = c("Unpopulated", "Populated", "Default"), ordered = TRUE)) 

write_csv(data.pop, args[3])

# repeat for copy so that it works with ggplot2
cables.assets.copy[cables.assets.copy == ""] <-  NA
Unpopulated <- apply(cables.assets.copy, 2, function(x) (mean(is.na(x)))*100)
Default <- apply(cables.assets.copy, 2, function(x) (mean(x %in% c("Default", "default", "DEFAULT")))*100)
Default <- ifelse(is.na(Default), 0, Default)
Populated <- 100 - Unpopulated - Default
Field <- names(Unpopulated)
data.pop <- data.frame(Field, Unpopulated, Populated, Default)
data.pop <- gather(data.pop, variable, value, -Field) %>%
  mutate(variable = factor(variable, levels = c("Unpopulated", "Populated", "Default"), ordered = TRUE)) 

ggplot(data = data.pop, aes(x = Field, y = value, fill = variable)) + 
    geom_bar(stat = "identity") + coord_flip() +
  labs(main = "Percentage Population", y="Percentage", fill="Population Levels")
```

## Asset ID

Asset_Number is the unique identifier. There is a total of **`r length(cables.assets$Asset_Number)`** rows in the cables source data. There are **`r length(unique(cables.assets$Asset_Number))`** unique values for Asset_Number.

## Year Of Manufacture

```{r age, message=FALSE, warning=FALSE, echo=FALSE}
PlotFdist(as.integer(as.numeric(cables.assets$Year_Of_Manufacture)), na.rm = TRUE,
          main = "Distribution of 10/15kV Cables by Year Of Manufacture")
```

## Voltage Duty Factor

```{r voltage duty, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=Voltage_Duty_Factor)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Voltage Duty Factor", x="Voltage Duty Factor", y="Count")
```

## Utilisation Duty Factor

```{r utilisation duty, message=FALSE, warning=FALSE, echo=FALSE}



ggplot(cables.assets, aes(x=Utilisation_Duty_Factor)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Utilisation Duty Factor", x="Utilisation Duty Factor", y="Count")
```

## SubDivision

```{r subdivision, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=`SubDivision`)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by SubDivision", x="SubDivision", y="Count")
```

## Cable Safety Rating

```{r cable safety, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=`Cable_Safety_Rating`)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Cable Safety Rating", x="Cable Safety Rating", y="Count")
```

## Sheath Test

```{r sheath, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=`Sheath Test Factor`)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Sheath Test", x="Sheath Test", y="Count")
```

## Partial Discharge

```{r partial discharge, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=`Partial Discharge Factor`)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Partial Discharge", x="Partial Discharge", y="Count")
```

## Fault History

```{r fault history, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=`Fault History Factor`)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Fault History", x="Fault History", y="Count")
```

## Reliability Modifier

```{r rel mod, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=`Reliability Modifier`)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Reliability Modifier", x="Reliability Modifier", y="Count")
```

## Reliability Collar

```{r rel col, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(cables.assets, aes(x=`Reliability Collar`)) +
         geom_bar() +
        labs(title="Count of 10/15kV Cables by Reliability Collar", x="Reliability Collar", y="Count")
```

---

# **Creation of Model Asset Base**

```{r warning=FALSE, echo=FALSE, message = FALSE}
assets <- cables.assets
assets$Year_Of_Manufacture <- as.numeric(assets$Year_Of_Manufacture)
assets$Connected_Customers<- as.numeric(assets$Connected_Customers)
assets$`Quantity Resource`<- as.numeric(assets$`Quantity Resource`)
```

```{r model, warning=FALSE, echo=FALSE, message = FALSE}
raw.model.data <- data.frame(Area1 = "Trefor",
                          TYPE = "Cable",
                          Asset_Number = assets$Asset_Number,
                          Site = paste0(assets$From, " - ", assets$To),
                          Trefor_Group = "10/15kV Cables",
                          Health_Index_Asset_Category = assets$Health_Index_Asset_Category,
                          Asset_Register_Category = assets$Asset_Register_Category,
                          Voltage = gsub("\\s(.*)", "", assets$Asset_Register_Category),
                          Year_Of_Manufacture = assets$Year_Of_Manufacture,                                                
                          SubDivision = assets$SubDivision,
                          Trefor_Subdivision = ifelse(grepl("PEX", assets$SubDivision),
                                                      "PEX", 
                                                      ifelse(grepl("NOT DEFINED", assets$SubDivision),
                                                             "PEX", "APB")),
                          Utilisation_Duty_Factor = assets$Utilisation_Duty_Factor,
                          Voltage_Duty_Factor =  assets$Voltage_Duty_Factor,
                          Cable_Safety_Rating = assets$Cable_Safety_Rating,
                          Connected_Customers = assets$Connected_Customers,
                          `Type_Factor` = assets$`Type_Factor`,
                          `Top_30_Customers_Factor` = assets$`Top_30_Customers_Factor`,
                          `KVA_Band_Per_Customer` = assets$`KVA_Band_Per_Customer`,
                          `Customer_Sensitivity_Factor` = assets$`Customer_Sensitivity_Factor`,
                          `Quantity Resource` = assets$`Quantity Resource`/1000,
                          `Sheath Test Factor` = assets$`Sheath Test Factor`,
                          `Partial Discharge Factor`=assets$`Partial Discharge Factor`,
                          `Fault History Factor` = assets$`Fault History Factor`,
                          `Reliability Modifier` = assets$`Reliability Modifier`,	
                          `Reliability Collar` = assets$`Reliability Collar`,
check.names = F, stringsAsFactors = F)
                          
table.data <- data.frame(`Model Field Name` = colnames(raw.model.data),
                         `Data Used` = c("'Trefor' for all assets",
                                         "'Cable' for all assets",
                                         "Asset_Number",
                                         "From - To",
                                         "10/15kV Cables",
                                         "Health_Index_Asset_Category",
                                         "Asset_Register_Category",
                                         "First word of the Asset_Register_Category",
                                         "Year_Of_Manufacture",
                                         "SubDivision",
                                         "Based on SubDivision",
                                         "Utilisation_Duty_Factor",
                                         "Voltage_Duty_Factor",
                                         "Cable_Safety_Rating",
                                         "Connected_Customers",
                                         "Type_Factor",
                                         "Top_30_Customers_Factor",
                                         "KVA_Band_Per_Customer",
                                         "Customer_Sensitivity_Factor",
                                         "Quantity_Ressource",
                                         "Sheath_Test_Factor",
                                         "Partial_Discharge_Factor",
                                         "Fault_History_Factor",
                                         "Reliability_Modifier",	
                                         "Reliability_Collar"), check.names = F)

kable(table.data, "html") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"))

model.data <- raw.model.data
```

```{r health category infill, warning=FALSE, echo=FALSE, message = FALSE}
model.accepts <- "HV UG Cable (Non-Pressurised)"
model.default <- "HV UG Cable (Non-Pressurised)"

model.data$Health_Index_Asset_Category[model.data$Health_Index_Asset_Category=="HV UG Cable (Non-Pressurised)"] <- "HV UG Cable (Non-Pressurised)"

health.category.default <- sum(!(model.data$Health_Index_Asset_Category %in% model.accepts))

model.data$Health_Index_Asset_Category <- ifelse(model.data$Health_Index_Asset_Category %in% model.accepts,
                                    model.data$Health_Index_Asset_Category,
                                    model.default)
```

```{r asset category infill, warning=FALSE, echo=FALSE, message = FALSE}
model.accepts <- c("10kV UG Cable (Non Pressurised)","15kV UG Cable (Non Pressurised)")
model.default <- "10kV UG Cable (Non Pressurised)"

asset.category.default <- sum(!(model.data$Asset_Register_Category %in% model.accepts))

model.data$Asset_Register_Category <- ifelse(model.data$Asset_Register_Category %in% model.accepts,
                                    model.data$Asset_Register_Category,
                                    model.default)
```

```{r subdivision category infill, warning=FALSE, echo=FALSE, message = FALSE}
model.accepts <- c("Lead sheath - Aluminium conductor","Lead sheath - Copper conductor","PEX sheath - Aluminium conductor","PEX sheath - Copper conductor")
model.default <- "PEX sheath - Aluminium conductor"

subdivision.default <- sum(!(model.data$SubDivision %in% model.accepts))

model.data$SubDivision <- ifelse(model.data$SubDivision %in% model.accepts,
                                    model.data$SubDivision,
                                    model.default)
```

```{r voltage infill, warning=FALSE, echo=FALSE, message = FALSE}
model.accepts <-c("10kV","15kV")
model.default <- "10kV"

voltage.default <- sum(!(model.data$Voltage %in% model.accepts))

model.data$Voltage <- ifelse(model.data$Voltage %in% model.accepts,
                                    model.data$Voltage,
                                    model.default)
```

```{r year infill, warning=FALSE, echo=FALSE, message = FALSE}
model.default <- 2001# model cannot run with this! Will need a default - done below

year.default <- sum(is.na(as.numeric(model.data$Year_Of_Manufacture)))

# change NA year values to average across asset base; 0 is used as a default value, so change this to NA
model.data$Year_Of_Manufacture[model.data$Year_Of_Manufacture==0 | cables.assets.copy$Year_Of_Manufacture=="Default" ] <- NA
model.data$Year_Of_Manufacture <- as.numeric(model.data$Year_Of_Manufacture)
model.data$Year_Of_Manufacture[is.na(model.data$Year_Of_Manufacture)] <- round(mean(model.data$Year_Of_Manufacture, na.rm=T))

model.data$Year_Of_Manufacture <- ifelse(!is.na(as.numeric(model.data$Year_Of_Manufacture)),
                                    model.data$Year_Of_Manufacture,
                                    model.default)
```


```{r utilisation duty infill, warning=FALSE, echo=FALSE, message = FALSE}
# model.data$Utilisation_Duty_Factor <- toupper(model.data$Utilisation_Duty_Factor)
# model.data$Utilisation_Duty_Factor[model.data$Utilisation_Duty_Factor %in% c("NORMAL/LOW")] <- 1
# model.data$Utilisation_Duty_Factor[model.data$Utilisation_Duty_Factor %in% c("HIGH", "HIGH (EG: AUTO-RECLOSERS)")] <- 1.2
# 
# model.accepts <- c(1, 1.2)
model.data$Utilisation_Duty_Factor <- toupper(model.data$Utilisation_Duty_Factor)

model.default <- 1

model.data$`Utilisation_Duty_Factor` <- as.numeric(model.data$`Utilisation_Duty_Factor`)

utilisation.duty.default  <- sum(is.na(model.data$`Utilisation_Duty_Factor`))

model.data$Utilisation_Duty_Factor <- ifelse(model.data$Utilisation_Duty_Factor <= .50, 0.8, ifelse(model.data$Utilisation_Duty_Factor > .50 & model.data$Utilisation_Duty_Factor <=.70, 0.9, ifelse(model.data$Utilisation_Duty_Factor > .70 & model.data$Utilisation_Duty_Factor <= 1, 1, ifelse(model.data$Utilisation_Duty_Factor > 1, 1.8, model.default))))


utilisation.duty.default <- utilisation.duty.default + sum(!is.na(model.data$Utilisation_Duty_Factor))

model.data$Utilisation_Duty_Factor <- ifelse(!is.na(as.numeric(model.data$Utilisation_Duty_Factor)),
                                    model.data$Utilisation_Duty_Factor,
                                    model.default)
```



```{r voltage duty infill, warning=FALSE, echo=FALSE, message = FALSE}
model.default <- 1

voltage.duty.default <- sum(is.na(as.numeric(model.data$Voltage_Duty_Factor)))

model.data$Voltage_Duty_Factor <- ifelse(model.data$Voltage_Duty_Factor>0 & model.data$Voltage_Duty_Factor<=0.4 & !is.na(model.data$Voltage_Duty_Factor), 0.7,
                                         ifelse(model.data$Voltage_Duty_Factor>0.4 & model.data$Voltage_Duty_Factor<=0.55 & !is.na(model.data$Voltage_Duty_Factor), 0.8,
                                                ifelse(model.data$Voltage_Duty_Factor>0.55 & model.data$Voltage_Duty_Factor<=0.7 & !is.na(model.data$Voltage_Duty_Factor), 0.9,
                                                       
ifelse(model.data$Voltage_Duty_Factor>0.7 & !is.na(model.data$Voltage_Duty_Factor), 1,model.default))))

# model.data$Voltage_Duty_Factor <- ifelse(!is.na(as.numeric(model.data$Voltage_Duty_Factor)),
#                                     model.data$Voltage_Duty_Factor,
#                                     model.default)
```

```{r cable safety infill, warning=FALSE, echo=FALSE, message = FALSE}
model.accepts <- c("Buried", "Exposed")
model.default <- "Buried"

cable.safety.default <- sum(!(model.data$Cable_Safety_Rating %in% model.accepts))

model.data$Cable_Safety_Rating <- ifelse(model.data$Cable_Safety_Rating %in% model.accepts,
                                    model.data$Cable_Safety_Rating,
                                    model.default)
```

```{r max demand infill, warning=FALSE, echo=FALSE, message = FALSE}

# # change 0 to NA as 0 is used as a default value
# model.data$Maximum_Demand[model.data$Maximum_Demand==0] <- NA

model.default <- mean(as.numeric(model.data$Connected_Customers), na.rm = T)
model.default <- ifelse(!is.na(model.default), model.default, 266)


max.demand.default <- sum(is.na(as.numeric(model.data$Connected_Customers)))

model.data$Connected_Customers <- ifelse(!is.na(as.numeric(model.data$Connected_Customers)),
                                    model.data$Connected_Customers,
                                    model.default)
```

```{r type infill, warning=FALSE, echo=FALSE, message = FALSE}
model.default <- 1

type.default <- sum(is.na(as.numeric(model.data$Type_Factor)))

model.data$Type_Factor <- ifelse(!is.na(as.numeric(model.data$Type_Factor)),
                                    model.data$Type_Factor,
                                    model.default)
```


```{r top 30 infill, warning=FALSE, echo=FALSE, message = FALSE}
model.accepts <- c(1,3)

model.default <- 1

top.30.default <- sum(is.na(as.numeric(model.data$Top_30_Customers_Factor)))

model.data$Top_30_Customers_Factor <- ifelse(!is.na(as.numeric(model.data$Top_30_Customers_Factor)),
                                    model.data$Top_30_Customers_Factor,
                                    model.default)
```




```{r KVA_Band Per Customer infill, warning=FALSE, echo=FALSE, message = FALSE}
model.accepts <- c("< 50", ">= 50 and < 100", ">= 100 and < 500", ">= 500 and < 1000", ">= 1000 and < 2000", ">=2000")
model.default <- "< 50"

model.data$KVA_Band_Per_Customer <- gsub(" ", "", model.data$KVA_Band_Per_Customer)
model.data$KVA_Band_Per_Customer <- gsub("and", " and ", model.data$KVA_Band_Per_Customer)
model.data$KVA_Band_Per_Customer <- gsub("<", "< ", model.data$KVA_Band_Per_Customer)
model.data$KVA_Band_Per_Customer <- gsub(">=", ">= ", model.data$KVA_Band_Per_Customer)
model.data$KVA_Band_Per_Customer <- gsub(">= 2000", ">=2000", model.data$KVA_Band_Per_Customer)

kva.default <- sum(!(model.data$KVA_Band_Per_Customer %in% model.accepts))

model.data$KVA_Band_Per_Customer <- ifelse(model.data$KVA_Band_Per_Customer %in% model.accepts,
                                    model.data$KVA_Band_Per_Customer,
                                    model.default)
```


```{r network infill, warning=FALSE, echo=FALSE, message = FALSE}
model.default <- 1

customer.sensitivity.default <- sum(is.na(as.numeric(model.data$Customer_Sensitivity_Factor)))

model.data$Customer_Sensitivity_Factor <- ifelse(!is.na(as.numeric(model.data$Customer_Sensitivity_Factor)),
                                    model.data$Customer_Sensitivity_Factor,
                                    model.default)
```

```{r quantity infill, warning=FALSE, echo=FALSE, message = FALSE}
model.default <- 1

quantity.default <- sum(is.na(as.numeric(model.data$`Quantity Resource`)))

model.data$`Quantity Resource` <- ifelse(!is.na(as.numeric(model.data$`Quantity Resource`)),
                                    model.data$`Quantity Resource`,
                                    model.default)
```

```{r sheath infill, warning=FALSE, echo=FALSE, message = FALSE}
model.data$`Sheath Test Factor` <- toupper(model.data$`Sheath Test Factor`)
model.data$`Sheath Test Factor`[model.data$`Sheath Test Factor` %in% c("PASS")] <- 1
model.data$`Sheath Test Factor`[model.data$`Sheath Test Factor` %in% c("FAILED MINOR")] <- 1.3
model.data$`Sheath Test Factor`[model.data$`Sheath Test Factor` %in% c("FAILED MAJOR")] <- 1.6

model.accepts <- c(1, 1.3, 1.6)
model.default <- 1

sheath.default <- sum(!(model.data$`Sheath Test Factor` %in% model.accepts) | model.data$`Sheath Test Factor` == "DEFAULT")

model.data$`Sheath Test Factor` <- ifelse(model.data$`Sheath Test Factor` %in% model.accepts,
                                            model.data$`Sheath Test Factor`,
                                            model.default)
```

```{r partial discharge infill, warning=FALSE, echo=FALSE, message = FALSE}
model.data$`Partial Discharge Factor` <- toupper(model.data$`Partial Discharge Factor`)
model.data$`Partial Discharge Factor`[model.data$`Partial Discharge Factor` %in% c("LOW")] <- 1
model.data$`Partial Discharge Factor`[model.data$`Partial Discharge Factor` %in% c("MEDIUM")] <- 1.15
model.data$`Partial Discharge Factor`[model.data$`Partial Discharge Factor` %in% c("HIGH")] <- 1.5

model.accepts <- c(1, 1.15, 1.5)
model.default <- 1

partialDischarge.default <- sum(!(model.data$`Partial Discharge Factor` %in% model.accepts) | model.data$`Partial Discharge Factor` == "DEFAULT")

model.data$`Partial Discharge Factor` <- ifelse(model.data$`Partial Discharge Factor` %in% model.accepts,
                                            model.data$`Partial Discharge Factor`,
                                            model.default)
```

```{r fault history infill, warning=FALSE, echo=FALSE, message = FALSE}
model.data$`Fault History Factor` <- toupper(model.data$`Fault History Factor`)
model.data$`Fault History Factor`[model.data$`Fault History Factor` %in% c("NO HISTORIC FAULTS RECORDED")] <- 1
model.accepts <- c(1, 1.3, 1.6, 1.8)
model.default <- 1

model.data$`Fault History Factor` <- as.numeric(model.data$`Fault History Factor`)

faultHistory.default <- sum(is.na(model.data$`Fault History Factor`))

model.data$`Fault History Factor` <- ifelse(model.data$`Fault History Factor`<0.01 & !is.na(model.data$`Fault History Factor`), 1.3,
                                         ifelse(model.data$`Fault History Factor`>=0.01 & model.data$`Fault History Factor`<0.1 & !is.na(model.data$`Fault History Factor`), 1.6,
                                                ifelse(model.data$`Fault History Factor`>=0.1 & !is.na(model.data$`Fault History Factor`),1.8,
                                                       model.default)))

faultHistory.default <- faultHistory.default + sum(!(model.data$`Fault History Factor` %in% model.accepts))

model.data$`Fault History Factor` <- ifelse(model.data$`Fault History Factor` %in% model.accepts,
                                            model.data$`Fault History Factor`,
                                            model.default)
```

```{r rel mod infill, warning=FALSE, echo=FALSE, message = FALSE}
model.default <- 1

reliability.modifier.default <- sum(is.na(as.numeric(model.data$`Reliability Modifier`)))
reliability.modifier.outside.range <- sum(model.data$`Reliability Modifier` < 0.6 | model.data$`Reliability Modifier` > 1.5)
reliability.modifier.outside.range <- ifelse(is.na(reliability.modifier.outside.range), 0, reliability.modifier.outside.range)

model.data$`Reliability Modifier` <- pmin(pmax(model.data$`Reliability Modifier`, 0.6), 1.5)

model.data$`Reliability Modifier` <- ifelse(!is.na(as.numeric(model.data$`Reliability Modifier`)),
                                    model.data$`Reliability Modifier`,
                                    model.default)
```

```{r rel col infill, warning=FALSE, echo=FALSE, message = FALSE}
model.default <- 0.5

reliability.collar.default <- sum(is.na(as.numeric(model.data$`Reliability Collar`)))

model.data$`Reliability Collar` <- ifelse(!is.na(as.numeric(model.data$`Reliability Collar`)),
                                    model.data$`Reliability Collar`,
                                    model.default)
```

## Default Counts

Any fields which are infilled during the process are assessed for default values below. Additionally, `r reliability.modifier.outside.range` cables are outside the required range of 0.6 to 1.5.

```{r summary, warning=FALSE, echo=FALSE, message = FALSE}
columns.infilled <- unique(names(model.data))[!(unique(names(model.data)) %in% c("Area1", "TYPE", "Trefor_Group", "Asset_Number", "Site", "Trefor_Subdivision"))]

infilling.summary <- data.frame(`Model Name` = columns.infilled,
                                `Asset Count Default` = c(health.category.default,
                                                          asset.category.default,
                                                          voltage.default,
                                                          year.default,
                                                          subdivision.default,
                                                          utilisation.duty.default,
                                                          voltage.duty.default,
                                                          cable.safety.default,
                                                          max.demand.default,
                                                          type.default,
                                                          top.30.default,
                                                          kva.default ,
                                                          customer.sensitivity.default,
                                                          quantity.default,
                                                          sheath.default,
                                                          partialDischarge.default,
                                                          faultHistory.default,
                                                          reliability.modifier.default,
                                                          reliability.collar.default), check.names = F)

kable(infilling.summary, "html") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"))
```

```{r export, warning=FALSE, echo=FALSE, message = FALSE}

write_csv(model.data, args[4])

```